Photographic Text-to-Image Synthesis \\ with a Hierarchically-nested Adversarial Network

### 2017-11-17 cvpr2018.tex
submit verison

%%%%%%%%% ABSTRACT
\begin{abstract}
This paper presents a novel method to deal with the challenging task of generating photographic images conditioned on semantic image descriptions.
Our method introduces accompanying hierarchical-nested adversarial objectives inside the network hierarchies, which regularize mid-level representations and assist generator training to capture the complex image statistics. We present an extensile single-stream generator architecture to better adapt the jointed discriminators and push generated images up to high resolutions. We adopt a multi-purpose adversarial loss to encourage more effective image and text information usage in order to improve the semantic consistency and image fidelity simultaneously. Furthermore, we introduce a new visual-semantic similarity measure to evaluate the semantic consistency of generated images, which also alleviates the cost of human evaluation. With extensive experimental validation on three public datasets, our method significantly improves previous state of the arts on all datasets over different evaluation metrics.

@@

%%%%%%%%% BODY TEXT
\section{Introduction}
Photographic text-to-image synthesis is a significant problem in generative model research \cite{reed2016generative}, which aims to learn a mapping from a semantic text space to a complex RGB image space. This task requires the generated images to be not only realistic but also \textit{semantically consistent}, for example, the generated images should preserve the object shape and color information described in the text.

@@

\begin{figure}[t]
%    \begin{center}
    \centering
    \begin{subfigure}[t]{0.5\textwidth}
    %    \centering
        \includegraphics[width=0.95\textwidth]{figure/intro2.pdf}
    \end{subfigure} \\
\centering
    \begin{subfigure}[t]{0.5\textwidth}
    %    \centering
        \includegraphics[width=0.95\textwidth,height=0.55\textwidth]{figure/single_view.pdf}
    \end{subfigure}
    \vspace{-.6cm}
    \caption{Top: Overview of our hierarchically-nested adversarial network. Bottom: Two generated results where fine-grained details are highlighted. \label{fig:intro}}     
    \vspace{-.5cm}
    %\end{center}
\end{figure}

%\begin{figure}[t]
%    \centering
%    \includegraphics[width=0.4\textwidth]{figure/intro.pdf}
%    \vspace{-.3cm}
%    \caption{Overview of our hierarchically-nested adversarial network. It contains a single-stream generator and several nested discriminators along the depth dimension of the generator, which can generate high-resolution images conditioned on a sentence.} \label{fig:archs-review} \vspace{-.3cm}
%\end{figure}
%\begin{figure}[t]
%    \centering
%    \includegraphics[width=0.4\textwidth]{figure/single_view.pdf}
%    \vspace{-.3cm}
%    \caption{Overview of our hierarchically-nested adversarial network. It contains a single-stream generator and several nested discriminators along the depth dimension of the generator, which can generate high-resolution images conditioned on a sentence.} \label{fig:archs-review} \vspace{-.3cm}
%\end{figure}
Recently, Generative adversarial networks (GANs) have become the main solution to this task. 
Reed \etal \cite{reed2016generative} address this task through a GAN based framework. But this method only scales up to $64^2$ resolution and can barely generate vivid object details.
Based on this method, StackGAN  \cite{han2017stackgan} propose a two-stage training strategy to generate high-resolution $256^2$ images. But this method requires training two separate GANs.  Later on, \cite{dong2017semantic} proposes to bypass the difficulty of learning mappings from vector embeddings to RGB images and treat it as a pixel-to-pixel translation problem \cite{isola2016image}. It works by re-rendering an arbitrary-style $128^2$ training image conditioned on a targeting description. However, its high-resolution synthesis capability remains unclear.

This paper pays attention to two major difficulties for text-to-image synthesis with GANs. The first is balancing the convergence between generators and discriminators \cite{goodfellow2014generative,improvedGAN}, which is actually a long-term problem in GANs. The second is stably modeling the huge pixel space in high-resolution images and guaranteeing semantic consistency \cite{han2017stackgan}. 
An effective strategy to regularize generators is critical to stabilize the training and help capture the complex image statistics \cite{huang2016stacked}.

In this paper, we propose a novel end-to-end method that can directly model high-resolution image statistics and generate semantically consistent and photographic images (see Figure \ref{fig:intro}). The contributions are described as follows.

Our generator resembles a simple vanilla GAN, without requiring multi-stage training and multiple internal text conditioning like \cite{han2017stackgan} or additional class label supervision like \cite{dash2017tac}. To tackle the problem of the big leap from the text space to the high-resolution image space, our insight is to leverage and regularize hierarchical representations with additional `deep' adversarial constraints. 
We introduce accompanying hierarchically-nested discriminators at multi-scale intermediate layers to play adversarial games and jointly encourage the generator approaching the real training data distribution. 
We also propose a new convolutional neural network (CNN) design for the generator to support accompanying discriminators more effectively in an end-to-end training manner.
To guarantee the image diversity and semantic consistency, we enforce discriminators at multiple side outputs of the generator to simultaneously differentiate real-and-fake image-text pairs as well as real-and-fake local image patches. %For more details, please refer to Section~\ref{sec:localloss}%focal

@@

We validate our proposed method on three datasets, CUB birds \cite{welinder2010caltech}, Oxford-102 flowers \cite{Nilsback08}, and large-scale MSCOCO \cite{lin2014microsoft}. In complement of existing evaluation metric (e.g. Inception score \cite{improvedGAN}) for generative models, we also introduce a new visual-semantic similarity metric to evaluate the alignment between generated images and conditioned text. Extensive experimental results and analysis demonstrate the effectiveness of our method and significantly improved performance compared against previous state of the arts on all three evaluation metrics.

@@

Deep generative models have attracted wide interests recently, including GANs \cite{goodfellow2014generative}, Variational Auto-encoders (VAE) \cite{kingma2013auto}, etc \cite{oord2016pixel}. 
There are substantial existing methods investigating better usage of GANs for different applications, such as image synthesis \cite{radford2015unsupervised, shrivastava2016learning}, (unpaired) pixel-to-pixel translation \cite{isola2016image,zhu2017unpaired}, medical applications \cite{costa2017towards}, etc \cite{ledig2016photo,huang2016stacked}.

Text-to-image synthesis is an interesting application of GANs. Reed \etal \cite{reed2016generative}  first introduce a method that can generate $64^2$ resolution images, which is similar with DCGAN \cite{radford2015unsupervised}. This method presents a new strategy for image-text matching aware adversarial training. Reed \etal \cite{reed2016learning} propose a generative
adversarial what-where network (GAWWN) to enable location and content instructions in text-to-image synthesis. StackGAN \etal \cite{han2017stackgan} propose a two-stage stacking GAN training approach that is able to generate $256^2$ compelling images. Recently, Dong \etal \cite{dong2017semantic} propose to learn a joint embedding of images and text so as to re-render a prototype image conditioned on a targeting description. Cha \etal \cite{char2017perceptual} explore the usage of the perceptional loss \cite{johnson2016perceptual} with a CNN pretrained on ImageNet  and Dash \etal \cite{dash2017tac} make use of auxiliary classifiers (similar with \cite{odena2016conditional}) to assist GAN training for text-to-image synthesis.

Learning a continuous mapping from a low-dimensional embedding manifold to a complex real data distribution is a long-standing problem. Although GANs have made significant progress, there are still many unsolved difficulties, e.g. training instability and high-resolution generation. Wide methods have been proposed to address the training instability, such as various training techniques \cite{salimans2016improved,arjovsky2017wasserstein,berthelot2017began,shrivastava2016learning,odena2016conditional}, regularization using extra knowledge (e.g. image labels, ImageNet CNNs, etc) \cite{dosovitskiy2016generating,ledig2016photo,dash2017tac,dash2017tac}, or different generator and discriminator combinations  \cite{metz2016unrolled,durugkar2016generative,yang2017lr,huang2016stacked}. \textit{While our method shows a new way to unite generators and discriminators and does not require any extra knowledge apart from training paired text and images.} In addition, it is easy to see the training difficulty increases significantly as the targeting image resolution increases.

@@

To synthesize high-resolution images, cascade networks are effective to decompose originally difficult tasks to multiple subtasks (Figure \ref{fig:archs-review} A).
Denton \etal \cite{denton2015deep} train a cascade of GANs in a Laplacian pyramid framework (LAPGAN) and use each to synthesize and refine image details and push up the output resolution stage-by-stage. StackGAN also shares some similar idea with LAPGAN. Inspired by this strategy, Chen \etal \cite{chen2017photographic} present a cascaded refinement network to synthesize high-resolution scene from semantic maps. 
%%% Huang \etal \cite{huang2016stacked} propose a top-down stacked GAN to leverage mid-level representations, which shares some similarities with StackGAN and our method. However, this method needs multiple symmetric bottom-up pre-trained discriminators and the usage of high-resolution image is unclear. 
Recently, Karras \etal \cite{Karras2017progressive} propose a progressive training of GANs. The idea is to add symmetric generator and discriminator layers gradually for high-resolution image generation (Figure \ref{fig:archs-review} C). \textit{Compared with these strategies that train low-to-high resolution GANs stage-by-stage or progressively, our method has the advantage of leveraging mid-level representations to encourage the integration of multiple subtasks, which makes end-to-end high-resolution image synthesis in a single vanilla-like GAN possible.}

@@

Leveraging hierarchical representations of neural networks is an effective way to enhance implicit multi-scaling and ensembling for tasks such as image recognition \cite{lee2015deeply} and pixel or object classification \cite{xie2015holistically,cai2016unified,long2015fully}. Particularly, using deep supervision \cite{lee2015deeply} in hierarchical convolutional layers provides short error paths and increases the discriminativeness of feature representations. 
\textit{Our hierarchically-nested adversarial objective is inspired by these families of deeply-supervised CNNs. }
%%%Our proposed hierarchically-nested adversarial supervision enhances layer representations to support final high resolution outputs.

@@

\subsection{Adversarial objective basics}
In brief, a GAN \cite{goodfellow2014generative} consists of a generator $G$ and a discriminator $D$, which are alternatively trained to compete with each other. $D$ is optimized to distinguish synthesized images from real images, meanwhile, $G$ is trained to fool $D$ by synthesizing fake images. Concretely, the optimal $G$ and $D$ can be obtained by playing the following two-player min-max game,

\begin{equation}
\label{equ:GAN}
\begin{split}
G^*, D^* = \arg~\underset{G}{\min}\ \underset{D}{\max}~ \mathcal{V}(D, G, Y, \bm z),
\end{split}
\end{equation}
where $Y$ and $\bm z \sim \mathcal{N}(0,1)$ denote training images and random noises, respectively. 
%$G$ is learned to approximate $G(\bm z) \sim p(Y)$.  The loss $\mathcal{L}$ for the valuation function is usually a cross-entropy loss, such that $\mathcal{V}(\cdot) = - \mathcal{L}(\cdot)$. 
$\mathcal{V}$ is the overall GAN objective, which usually takes the form $\mathbb{E}_{Y\sim p_{data}}\big[\log D(Y)\big] + \mathbb{E}_{\bm z\sim p_{z}}\big[\log (1-D(G(\bm z)))\big]$ (cross-entropy loss) or other variations \cite{lsgan,berthelot2017began}.

@@

\subsection{Hierarchical-nested adversarial objectives}
Numerous GAN methods have demonstrated ways to unite generators and discriminators for image synthesis. Figure \ref{fig:archs-review} and Section 2 discuss some typical frameworks.
Our method actually explores a new dimension of playing this adversarial game along the depth of a generator (Figure \ref{fig:archs-review} D), which integrates additional hierarchical-nested discriminators at intermediate layers of the generator. 
The proposed objectives act as regularizers to the hidden space of $\mathcal{G}$, which also offer a short path for better error signal flow and helps reduce the training instability.

The proposed $\mathcal{G}$ is a CNN (defined in Section 3.4) producing multiple outputs with gradually increasing size:
%This architecture resemble the proposed inverse architectures in edge detection\cite{xie2015holistically} and classification \cite{lee2015deeply}, which demonstrate that additional supervision to hidden layers can improve model generalization and boost optimization.  
\begin{equation}
\label{side}
X_1,..., X_s = \mathcal{G}(\bm t, \bm z), 
\end{equation}
where  $\bm t\sim p_{data}$ denotes a sentence embedding (generated by a pre-trained char RNN text encoder\cite{reed2016generative}). $\mathcal{G}$ produces $s-1$ side outputs $\{X_1,...,X_{s-1}\}$  and one final output $X_s$ with the highest resolution.

@@

For each side output $X_i$ from the generator, a distinct discriminator $D_i$ is associated to compete with it. Therefore, our full min-max objective is defined as 
\begin{equation}
\label{equ:optim}
\begin{split}
  \mathcal{G}^*, \mathcal{D}^*&  =  \arg~\underset{\mathcal{G}}{\min}\ \underset{\mathcal{D}}{\max}~ \mathcal{V}(\mathcal{G},\mathcal{D}, \mathcal{Y}, \bm t, \bm z), \\
  %\text{where} \;\;     \mathcal{D} & =  \{D_1, ..., D_s\}, \; \mathcal{Y} = \{Y_1, ..., Y_s\},
\end{split}
\end{equation}
where $\mathcal{D}  =  \{D_1, ..., D_s\} $ and $\; \mathcal{Y} = \{Y_1, ..., Y_s\}$ denotes one training image at multi-scales, $\{1,...,s\}$, forming an image pyramid.
Compared with Eq. (\ref{equ:GAN}), our generator competes with multiple discriminators  $\{D_i\}$ at different hierarchies (Figure \ref{fig:archs-review} D), each focuses on learning discriminative features in different contextual scale.

In principle, the lower-resolution side output is used to learn semantic consistent image structures (e.g. object shape, colors, and background), and the subsequent higher-resolution side outputs are used to render fine-grained details. Since our method is trained in an end-to-end fashion, the lower-resolution outputs can also fully utilize top-down knowledge from discriminators at higher resolutions. As a result, we can observe consistent image structures, color and styles in outputs of both low and high resolutions without using addition regularization terms.

@@

To alleviate these issues and guarantee image fidelity, our solution is to add local adversarial image losses.
%as inspired by \cite{shrivastava2016learning}. 
%The insights are two folds:
%\begin{itemize}\vspace{-.1cm}
%\setlength\itemsep{-0.3em}
%\item Further forcing the generated samples to have only global but also local similar statistics to real image patches, which is beneficial for rendering fine-grained details. 
%
%\item \textcolor{red}{Image loss without using paired text can be beneficial in the sense that it focuses more on image information. The richness of discriminator supervision usually has advantages for generalization. } 
%\vspace{-.2cm}
%\end{itemize}
We expect the low-resolution discriminators to focus on global structures, while the high-resolution discriminators to focus on local image details.
Each discriminator $D_i$ consists of two branches (see Section 3.4), one computes a single scalar value for the pair loss and another branch computes  $R_i{\times}R_i$ 2D output maps $O_i$ for local image loss.
%with an extra branch of the discriminator for the pair loss (see Section 3.4).
%computes a $R{\times}R$ probability map. 
Each element in $O_i$ differentiates whether a corresponding local image patch is real or fake.
For each $D_i$, we control $R_i$ accordingly to tune the receptive field of each element of $O_i$. 
%In practice, the local image adversarial loss can be implemented as a fully CNN \cite{shrivastava2016learning,zhu2017unpaired,isola2016image}. 
Figure \ref{fig:loss} illustrates how hierarchically-nested discriminators compute the two losses on the generated images in the pyramid.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=0.49\textwidth]{figure/loss.pdf}
    \vspace{-.7cm}
    \caption{Given a set of images from the side output pyramid of the generator, the corresponding discriminator $D_i$ computes the matching-aware pair loss and local image loss (outputting a $R_i{\times}R_i$ probability map to classify real or fake image patches). }  \vspace{-.2cm}
    \label{fig:loss}
\end{figure}

\textbf{Full Objective } Overall, our full min-max adversarial objective can be defined as 
%%hierarchically-nested discriminators $\{D_i\}$ optimize the following objective:
\vspace{-.2cm}
\begin{equation}
\begin{split}
\mathcal{V}(& \mathcal{G},\mathcal{D}, \mathcal{Y}, \bm t, \bm z) = \sum_{i=1}^{s} \Big(  L_2\big(D_i({Y}_i)\big) +  L_2\big(D_i({Y}_i, \bm t_{Y})\big) \, + \\ 
& \overline{L_2}\big(D_i({X}_i)\big)  + \overline{L_2}\big(D_i({X}_i, \bm{t}_{X_i})\big) + \overline{L_2}\big(D_i({Y}_i,  \bm{t}_{\overline{Y}})\big) \Big),
\end{split}
\end{equation}
where $L_2(x) = \mathbb{E}\big[(x - \mathbb{I})^2\big]$ is the mean-square loss (instead of the conventional cross-entropy loss) and $\overline{L_2}(x) =\mathbb{E}\big[x^2\big]$. 
This objective is directly minimized by $\mathcal{D}$. For generator $\mathcal{G}$ in practice, we minimize 
$\sum_{i=1}^{s} (L_2(D_i(\mathcal{G}(\bm t, \bm z)_i)) +  L_2\big(D_i(\mathcal{G}(\bm t, \bm z)_i, \bm{t}_{X_i})))$ instead.
For the local image loss, the shape of $x, \mathbb{I} \in \mathbb{R}^{R_i{\times}R_i}$ vary accordingly (see Figure \ref{fig:loss}). $R_i=1$ refers to the (largest local) global range. $D_i(X_i)$ is the image loss branch and $D_i(X_i, \bm{t}_{X_i})$ is the pair loss branch (conditioned on $\bm{t}_{X_i}$).
$\{Y_i, \bm t_{Y}\}$ denotes a matched image-text pair and $\{Y_i, \bm{t}_{\overline{Y}}\}$ denotes a mismatched image-text pair.

In the spirit of variational auto-encoder \cite{vae} and the practice of StackGAN \cite{han2017stackgan}, instead of directly using the deterministic text embedding, we sample a stochastic vector from a Ganssian distribution $\mathcal{N}(\mu({\bm t}), \Sigma({\bm t}))$, where $\mu$ and $\Sigma$ are parameterized functions of $\bm t$. 
We add the Kullback-Leibler divergence regularization term, $D_{KL}(\mathcal{N}(\mu({\bm t}), \Sigma({\bm t}) )|| \mathcal{N}(0, \bm{I}))$, to the GAN objective to prevent over-fitting and force smooth sampling over the text embedding distribution.

>>>>

%%%%%%%%% ABSTRACT
\begin{abstract}
This paper presents a novel method to deal with the challenging task of generating photographic images conditioned on semantic image descriptions.
Our method introduces accompanying hierarchical-nested adversarial objectives inside the network hierarchies, which regularize mid-level representations and assist generator training to capture the complex image statistics. We present an extensile single-stream generator architecture to better adapt the jointed discriminators and push generated images up to high resolutions. We adopt a multi-purpose adversarial loss to encourage more effective image and text information usage in order to improve the semantic consistency and image fidelity simultaneously. Furthermore, we introduce a new visual-semantic similarity measure to evaluate the semantic consistency of generated images. With extensive experimental validation on three public datasets, our method significantly improves previous state of the arts on all datasets over different evaluation metrics.

@@

%%%%%%%%% BODY TEXT
\section{Introduction}
Photographic text-to-image synthesis is a significant problem in generative model research \cite{reed2016generative}, which aims to learn a mapping from a semantic text space to a complex RGB image space. This task requires the generated images to be not only realistic but also \textit{semantically consistent}, i.e., the generated images should preserve specific object sketches and semantic details described in text.

@@

\begin{figure}[t]
%    \begin{center}
    \centering
    \begin{subfigure}[t]{0.5\textwidth}
    %    \centering
        \includegraphics[width=0.95\textwidth]{figure/intro2.pdf}
    \end{subfigure} \\
\centering
    \begin{subfigure}[t]{0.5\textwidth}
    %    \centering
        \includegraphics[width=0.95\textwidth,height=0.55\textwidth]{figure/single_view.pdf}
    \end{subfigure}
    \vspace{-.6cm}
    \caption{Top: Overview of our hierarchically-nested adversarial network, which produces side output images with growing resolutions. Each side output is associated with a discriminator. Bottom: Two test sample results where fine-grained details are highlighted. \label{fig:intro}}     
    \vspace{-.5cm}
    %\end{center}
\end{figure}

%\begin{figure}[t]
%    \centering
%    \includegraphics[width=0.4\textwidth]{figure/intro.pdf}
%    \vspace{-.3cm}
%    \caption{Overview of our hierarchically-nested adversarial network. It contains a single-stream generator and several nested discriminators along the depth dimension of the generator, which can generate high-resolution images conditioned on a sentence.} \label{fig:archs-review} \vspace{-.3cm}
%\end{figure}
%\begin{figure}[t]
%    \centering
%    \includegraphics[width=0.4\textwidth]{figure/single_view.pdf}
%    \vspace{-.3cm}
%    \caption{Overview of our hierarchically-nested adversarial network. It contains a single-stream generator and several nested discriminators along the depth dimension of the generator, which can generate high-resolution images conditioned on a sentence.} \label{fig:archs-review} \vspace{-.3cm}
%\end{figure}

Recently, Generative adversarial networks (GANs) have become the main solution to this task. 
Reed \etal \cite{reed2016generative} address this task through a GAN based framework. But this method only generates $64^2$ images and can barely generate vivid object details.
Based on this method, StackGAN \cite{han2017stackgan} proposes to stack another low-to-high resolution GAN to generate $256^2$ images. But this method requires training two separate GANs. Later on, \cite{dong2017semantic} proposes to bypass the difficulty of learning mappings from text to RGB images and treat it as a pixel-to-pixel translation problem \cite{isola2016image}. It works by re-rendering an arbitrary-style $128^2$ training image conditioned on a targeting description. 
However, its high-resolution synthesis capability is unclear. 
At present, training a generative model to map from a low-dimensional text space to a high-resolution image space in a fully end-to-end manner still remains unsolved.

This paper pays attention to two major difficulties for text-to-image synthesis with GANs. The first is balancing the convergence between generators and discriminators \cite{goodfellow2014generative,improvedGAN}, which is a common problem in GANs. The second is stably modeling the huge pixel space in high-resolution images and guaranteeing semantic consistency \cite{han2017stackgan}. 
An effective strategy to regularize generators is critical to stabilize the training and help capture the complex image statistics \cite{huang2016stacked}.

In this paper, we propose a novel end-to-end method that can directly model high-resolution image statistics and generate photographic images (see Figure \ref{fig:intro} bottom). The contributions are described as follows.

Our generator resembles a simple vanilla GAN, without requiring multi-stage training and multiple internal text conditioning like \cite{han2017stackgan} or additional class label supervision like \cite{dash2017tac}. To tackle the problem of the big leap from the text space to the image space, our insight is to leverage and regularize hierarchical representations with additional `deep' adversarial constraints (see Figure \ref{fig:intro} top). 
We introduce accompanying hierarchically-nested discriminators at multi-scale intermediate layers to play adversarial games and jointly encourage the generator to approach the real training data distribution. 
We also propose a new convolutional neural network (CNN) design for the generator to support accompanying discriminators more effectively.
To guarantee the image diversity and semantic consistency, we enforce discriminators at multiple side outputs of the generator to simultaneously differentiate real-and-fake image-text pairs as well as real-and-fake local image patches. %%For more details, please refer to Section~\ref{sec:localloss}%focal

@@

We validate our proposed method on three datasets, CUB birds \cite{welinder2010caltech}, Oxford-102 flowers \cite{Nilsback08}, and large-scale MSCOCO \cite{lin2014microsoft}. In complement of existing evaluation metrics (e.g. Inception score \cite{improvedGAN}) for generative models, we also introduce a new visual-semantic similarity metric to evaluate the alignment between generated images and conditioned text. It alleviates the issue of the expensive human evaluation. Extensive experimental results and analysis demonstrate the effectiveness of our method and significantly improved performance compared against previous state of the arts on all three evaluation metrics.

@@

Deep generative models have attracted wide interests recently, including GANs \cite{goodfellow2014generative,radford2015unsupervised}, Variational Auto-encoders (VAE) \cite{kingma2013auto}, etc \cite{oord2016pixel}. 
There are substantial existing methods investigating the better usage of GANs for different applications, such as image synthesis \cite{radford2015unsupervised, shrivastava2016learning}, (unpaired) pixel-to-pixel translation \cite{isola2016image,zhu2017unpaired}, medical applications \cite{costa2017towards}, etc \cite{ledig2016photo,huang2016stacked}.

Text-to-image synthesis is an interesting application of GANs. Reed \etal \cite{reed2016generative} is the first to introduce a method that can generate $64^2$ resolution images. This method also presents a new strategy for image-text matching aware adversarial training. Reed \etal \cite{reed2016learning} propose a generative
adversarial what-where network (GAWWN) to enable location and content instructions in text-to-image synthesis. Zhang \etal \cite{han2017stackgan} propose a two-stage training strategy that is able to generate $256^2$ compelling images. Recently, Dong \etal \cite{dong2017semantic} propose to learn a joint embedding of images and text so as to re-render a prototype image conditioned on a targeting description. Cha \etal \cite{char2017perceptual} explore the usage of the perceptional loss \cite{johnson2016perceptual} with a CNN pretrained on ImageNet  and Dash \etal \cite{dash2017tac} make use of auxiliary classifiers (similar with \cite{odena2016conditional}) to assist GAN training for text-to-image synthesis.

Learning a continuous mapping from a low-dimensional manifold to a complex real image distribution is a long-standing problem. Although GANs have made significant progress, there are still many unsolved difficulties, e.g., training instability and high-resolution generation. Wide methods have been proposed to address the training instability, such as various training techniques \cite{salimans2016improved,arjovsky2017wasserstein,berthelot2017began,shrivastava2016learning,odena2016conditional}, regularization using extra knowledge (e.g. image labels, ImageNet CNNs, etc) \cite{dosovitskiy2016generating,ledig2016photo,dash2017tac,dash2017tac}, or different generator and discriminator combinations  \cite{metz2016unrolled,durugkar2016generative,yang2017lr,huang2016stacked}. \textit{While our method shows a new way to unite generators and discriminators and does not require any extra knowledge apart from training paired text and images.} In addition, it is easy to see the training difficulty increases significantly as the targeting image resolution increases.

@@

To synthesize high-resolution images, cascade networks are effective to decompose originally difficult tasks to multiple subtasks (Figure \ref{fig:archs-review} A).
Denton \etal \cite{denton2015deep} train a cascade of GANs in a Laplacian pyramid framework (LAPGAN) and use each to synthesize and refine image details and push up the output resolution stage-by-stage. StackGAN also shares similar ideas with LAPGAN. Inspired by this strategy, Chen \etal \cite{chen2017photographic} present a cascaded refinement network to synthesize high-resolution scenes from semantic maps. 
%%% Huang \etal \cite{huang2016stacked} propose a top-down stacked GAN to leverage mid-level representations, which shares some similarities with StackGAN and our method. However, this method needs multiple symmetric bottom-up pre-trained discriminators and the usage of high-resolution image is unclear. 
Recently, Karras \etal \cite{Karras2017progressive} propose a progressive training of GANs. The idea is to add symmetric generator and discriminator layers gradually for high-resolution image generation (Figure \ref{fig:archs-review} C). \textit{Compared with these strategies that train low-to-high resolution GANs stage-by-stage or progressively, our method has the advantage of leveraging mid-level representations to encourage the integration of multiple subtasks, which makes end-to-end high-resolution image synthesis in a single vanilla-like GAN possible.}

@@

Leveraging hierarchical representations of CNNs is an effective way to enhance implicit multi-scaling and ensembling for tasks such as image recognition \cite{lee2015deeply} and pixel or object classification \cite{xie2015holistically,cai2016unified,long2015fully}. Particularly, using deep supervision \cite{lee2015deeply} at intermediate convolutional layers provides short error paths and increases the discriminativeness of feature representations. 
\textit{Our hierarchically-nested adversarial objective is inspired by the family of deeply-supervised CNNs.}
%%%Our proposed hierarchically-nested adversarial supervision enhances layer representations to support final high resolution outputs.

@@

\subsection{Adversarial objective basics}
In brief, a GAN \cite{goodfellow2014generative} consists of a generator $G$ and a discriminator $D$, which are alternatively trained to compete with each other. $D$ is optimized to distinguish synthesized images from real images, meanwhile, $G$ is trained to fool $D$ by synthesizing fake images. Concretely, the optimal $G$ and $D$ can be obtained by playing the following two-player min-max game,
\begin{equation}
\label{equ:GAN}
\begin{split}
G^*, D^* = \arg~\underset{G}{\min}\ \underset{D}{\max}~ \mathcal{V}(D, G, Y, \bm z),
\end{split}
\end{equation}
where $Y$ and $\bm z \sim \mathcal{N}(0,1)$ denote training images and random noises, respectively. 
%$G$ is learned to approximate $G(\bm z) \sim p(Y)$.  The loss $\mathcal{L}$ for the valuation function is usually a cross-entropy loss, such that $\mathcal{V}(\cdot) = - \mathcal{L}(\cdot)$. 
$\mathcal{V}$ is the overall GAN objective, which usually takes the form $\mathbb{E}_{Y\sim p_{data}}\big[\log D(Y)\big] + \mathbb{E}_{\bm z\sim p_{z}}\big[\log (1-D(G(\bm z)))\big]$ (cross-entropy loss) or other variations \cite{lsgan,berthelot2017began}.

@@

\subsection{Hierarchical-nested adversarial objectives}
Numerous GAN methods have demonstrated ways to unite generators and discriminators for image synthesis. Figure \ref{fig:archs-review} and Section 2 discuss some typical frameworks.
Our method actually explores a new dimension of playing this adversarial game along the depth of a generator (Figure \ref{fig:archs-review} D), which integrates additional hierarchical-nested discriminators at intermediate layers of the generator. 
The proposed objectives act as regularizers to the hidden space of $\mathcal{G}$, which also offer a short path for error signal flows and help reduce the training instability.

The proposed $\mathcal{G}$ is a CNN (defined in Section 3.4), which produces multiple side outputs:
%This architecture resemble the proposed inverse architectures in edge detection\cite{xie2015holistically} and classification \cite{lee2015deeply}, which demonstrate that additional supervision to hidden layers can improve model generalization and boost optimization.  
\begin{equation}
\label{side}
X_1,..., X_s = \mathcal{G}(\bm t, \bm z), 
\end{equation}
where  $\bm t\sim p_{data}$ denotes a sentence embedding (generated by a pre-trained char-RNN text encoder \cite{reed2016generative}). $\{X_1,...,X_{s-1}\}$ are images with gradually growing resolutions and $X_s$ is the final output with the highest resolution.

@@

For each side output $X_i$ from the generator, a distinct discriminator $D_i$ is used to compete with it. Therefore, our full min-max objective is defined as 
\begin{equation}
\label{equ:optim}
\begin{split}
  \mathcal{G}^*, \mathcal{D}^*&  =  \arg~\underset{\mathcal{G}}{\min}\ \underset{\mathcal{D}}{\max}~ \mathcal{V}(\mathcal{G},\mathcal{D}, \mathcal{Y}, \bm t, \bm z), \\
  %\text{where} \;\;     \mathcal{D} & =  \{D_1, ..., D_s\}, \; \mathcal{Y} = \{Y_1, ..., Y_s\},
\end{split}
\end{equation}
where $\mathcal{D} = \{D_1, ..., D_s\} $ and $\; \mathcal{Y} = \{Y_1, ..., Y_s\}$ denotes training images at multi-scales, $\{1,...,s\}$.
Compared with Eq. (\ref{equ:GAN}), our generator competes with multiple discriminators $\{D_i\}$ at different hierarchies (Figure \ref{fig:archs-review} D), which jointly learn discriminative features in different contextual scales.

In principle, the lower-resolution side output is used to learn semantic consistent image structures (e.g. object sketches, colors, and background), and the subsequent higher-resolution side outputs are used to render fine-grained details. Since our method is trained in an end-to-end fashion, the lower-resolution outputs can also fully utilize top-down knowledge from discriminators at higher resolutions. As a result, we can observe consistent image structures, color and styles in the outputs of both low and high resolution images. The experiment demonstrates this advantage compared with StackGAN.

@@

To alleviate these issues and guarantee image fidelity, our solution is to add local adversarial image losses.
We expect the low-resolution discriminators to focus on global structures, while the high-resolution discriminators to focus on local image details.
Each discriminator $D_i$ consists of two branches (see Section 3.4), one computes a single scalar value for the pair loss and another branch computes a $R_i{\times}R_i$ 2D probability map $O_i$ for the local image loss.
For each $D_i$, we control $R_i$ accordingly to tune the receptive field of each element in $O_i$, which 
differentiates whether a corresponding local image patch is real or fake.
The local GAN loss is also used for pixel-to-pixel translation tasks \cite{shrivastava2016learning,zhu2017unpaired,isola2016image}. 
Figure \ref{fig:loss} illustrates how hierarchically-nested discriminators compute the two losses on the generated images in the pyramid.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=0.49\textwidth]{figure/loss.pdf}
    \vspace{-.7cm}
    \caption{For each side out image in the pyramid from the generator, the corresponding discriminator $D_i$ computes the matching-aware pair loss and the local image loss (outputting a $R_i{\times}R_i$ probability map to classify real or fake image patches). }  \vspace{-.4cm}
    \label{fig:loss}
\end{figure}

\textbf{Full Objective } Overall, our full min-max adversarial objective can be defined as 
%%hierarchically-nested discriminators $\{D_i\}$ optimize the following objective:
\vspace{-.2cm}
\begin{equation}
\begin{split}
\mathcal{V}(& \mathcal{G},\mathcal{D}, \mathcal{Y}, \bm t, \bm z) = \sum_{i=1}^{s} \Big(  L_2\big(D_i({Y}_i)\big) +  L_2\big(D_i({Y}_i, \bm t_{Y})\big) \, + \\ 
& \overline{L_2}\big(D_i({X}_i)\big)  + \overline{L_2}\big(D_i({X}_i, \bm{t}_{X_i})\big) + \overline{L_2}\big(D_i({Y}_i,  \bm{t}_{\overline{Y}})\big) \Big),
\end{split} \vspace{-.6cm}
\end{equation}
where $L_2(x) = \mathbb{E}\big[(x - \mathbb{I})^2\big]$ is the mean-square loss (instead of the conventional cross-entropy loss) and $\overline{L_2}(x) =\mathbb{E}\big[x^2\big]$. 
This objective is minimized by $\mathcal{D}$. While in practice, $\mathcal{G}$ minimizes
$\sum_{i=1}^{s} (L_2(D_i(\mathcal{G}(\bm t, \bm z)_i)) +  L_2\big(D_i(\mathcal{G}(\bm t, \bm z)_i, \bm{t}_{X_i})))$ instead.
For the local image loss, the shape of $x, \mathbb{I} \in \mathbb{R}^{R_i{\times}R_i}$ varies accordingly (see Figure \ref{fig:loss}). $R_i=1$ refers to the (largest local) global range. $D_i(X_i)$ is the image loss branch and $D_i(X_i, \bm{t}_{X_i})$ is the pair loss branch (conditioned on $\bm{t}_{X_i}$).
$\{Y_i, \bm t_{Y}\}$ denotes a matched image-text pair and $\{Y_i, \bm{t}_{\overline{Y}}\}$ denotes a mismatched image-text pair.

In the spirit of variational auto-encoder \cite{vae} and the practice of StackGAN \cite{han2017stackgan} (termed conditioning augmentation (CA)), instead of directly using the deterministic text embedding, we sample a stochastic vector from a Ganssian distribution $\mathcal{N}(\mu({\bm t}), \Sigma({\bm t}))$, where $\mu$ and $\Sigma$ are parameterized functions of $\bm t$. 
We add the Kullback-Leibler divergence regularization term, $D_{KL}(\mathcal{N}(\mu({\bm t}), \Sigma({\bm t}) )|| \mathcal{N}(0, \bm{I}))$, to the GAN objective to prevent over-fitting and force smooth sampling over the text embedding distribution.
